Contribution Title\thanks{Supported by organization x.}

### 2019-10-23 paper/paper.tex
Turned figure 6 into a wrapfigure
Moved preliminaries to the appendix
Move wrapfig
Added short notations section

\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
%% \usepackage{subcaption} %% For complex figures with subfigures/subcaptions
%%                         %% http://ctan.org/pkg/subcaption
\usepackage{subfig}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{tikz}
\usetikzlibrary{arrows.meta,automata,calc}
\usepackage{tikz-qtree} % Used for syntax trees
\usepackage{tikz-cd} % Used for commutative diagrams
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}

@@

\section{Preliminaries}
\label{sec:prel}

This section briefly describes the theoretical foundations we build upon.

@@

@@

\begin{figure}
  \begin{tikzcd}
    L(T_D) \arrow[d, "\yield"] & L(T'_D) \arrow[l, "\semantic"'] \arrow[d, "\yield"] \\
    L(G_D) & L(G'_D)
  \end{tikzcd}
  \caption{The generated grammars, and their relation to each other.}
  \label{fig:grammar-square}
\end{figure}

@@

>>>>

\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
%% \usepackage{subcaption} %% For complex figures with subfigures/subcaptions
%%                         %% http://ctan.org/pkg/subcaption
\usepackage{subfig}
\usepackage{wrapfig}
\usepackage{multicol}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{tikz}
\usetikzlibrary{arrows.meta,automata,calc}
\usepackage{tikz-qtree} % Used for syntax trees
\usepackage{tikz-cd} % Used for commutative diagrams
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}

@@

\section{Notation}
\label{sec:prel}

This section briefly explains the notations used in this paper.
%
Given a context-free grammar $G$, we write $L(G)$ to denote the
set of all words recognized by $G$.
%
The standard definition of ambiguity states that a word
$w \in L(G)$ is ambiguous if there are two distinct leftmost
derivations of that word.
%
An automata is a 5-tuple $(Q,\T,\delta,q_0,F)$, where $Q$ is a
finite set of states; $\T$ a finite set of terminals; $\delta$ a
transition function from $Q \times \T$ to finite subsets of $Q$
(or single states of $Q$ for a deterministic automaton);
$q_0 \in Q$ an initial state; and $F \subseteq Q$ a set of final
states.
%
A pushdown automata further adds a set of stack symbols $\Gamma$
and equips the transition function $\delta$ with information on
which symbols are pushed, popped or just read from the stack.

Appendix~\ref{app:prel} contains a more detailed
description of the preliminaries (for reviewers).

@@

\begin{wrapfigure}{l}{0.3\textwidth}
  \begin{tikzcd}
    L(T_D) \arrow[d, "\yield"] & L(T'_D) \arrow[l, "\semantic"'] \arrow[d, "\yield"] \\
    L(G_D) & L(G'_D)
  \end{tikzcd}
  \caption{The generated grammars, and their relation to each other.}
  \label{fig:grammar-square}
\end{wrapfigure}

@@

@@

\appendix

\section{Preliminaries}
\label{app:prel}

This appendix briefly describes some of the theoretical
foundations we build upon.
